\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,xcolor}
\input{_macros}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}{Remark}

\newcommand{\R}{\mathbb{R}}
\newcommand{\norm}[1]{\left\lVert #1\right\rVert}
\newcommand{\rhor}[2]{\rho_{#1}^{(#2)}}

\title{Proof of Conjecture 3:\\
Strict Monotonicity of $\rho_p$ for the Hadamard Matrix}
\author{}
\date{}

\begin{document}
\maketitle

\section*{Statement}

\begin{theorem}[Conjecture 3]\label{thm:conj3}
For every integer $n>6$ and every integer $p>2$, there exists $M\in\mathbb{R}^{n\times n}$ such that
\[
\rho_p(M) < \rho_{p+1}(M),
\]
where $\rho_r(M):=\inf\bigl\{\|\Delta M\Delta^{-1}\|_{\ell^r_n\to\ell^r_n} \mid \Delta=\mathrm{diag}(\delta_1,\dots,\delta_n),\,\delta_i>0\bigr\}$.
\end{theorem}

The proof proceeds in four steps. We first establish a zero-padding lemma (Section~\ref{sec:padding}), then compute the exact $\ell^r$-operator norm of the normalized $4\times4$ Hadamard matrix (Section~\ref{sec:hadamard}), show that no diagonal scaling can improve this value (Section~\ref{sec:scaling}), and finally combine everything to prove Conjecture~3 (Section~\ref{sec:conclusion}).

%% ============================================================
\section{Zero-Padding Preserves $\rho_r$}
\label{sec:padding}
%% ============================================================

\input{section_1_final}

%% ============================================================
\section{Norm of the Normalized Hadamard Matrix}
\label{sec:hadamard}
%% ============================================================

\input{section_2_final}

%% ============================================================
\section{Diagonal Scalings Cannot Improve $H$}
\label{sec:scaling}
%% ============================================================

\input{section_3_final}

%% ============================================================
\section{Proof of Conjecture 3}
\label{sec:conclusion}
%% ============================================================

\input{section_4_final}

\begin{thebibliography}{9}
\bibitem{coron2008}
J.-M.\ Coron, G.\ Bastin, and B.\ d'Andr\'ea-Novel.
Dissipative boundary conditions for one-dimensional nonlinear hyperbolic systems.
\textit{SIAM J.\ Control Optim.}, 47(3):1460--1498, 2008.

\bibitem{coron2015}
J.-M.\ Coron and H.-M.\ Nguyen.
Dissipative boundary conditions for nonlinear 1-D hyperbolic systems: sharp conditions through an approach via time-delay systems.
\textit{SIAM J.\ Math.\ Anal.}, 47(3):2220--2240, 2015.

\bibitem{rump2003}
S.\ M.\ Rump.
Optimal scaling for $p$-norms and componentwise distance to singularity.
\textit{IMA J.\ Numer.\ Anal.}, 23(1):1--9, 2003.
\end{thebibliography}

\end{document}
